Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
Edits on experiment design.

\indent \indent We plan to simulate and test three distinct censorship environments
which vary in their methods of censorship and thus require distinct responses from our 
participants to circumvent successfully. These environments are designed with respect to 
common censorship techniques employed 
today along with knowledge of how pluggable transports will need to be used.
For instance, some of Tor's pluggable transports work in censorship environments
where others do not. Additionally, some of them require additional information (like bridge 
addresses) before they enable the user to successfully circumvent censorship. 
Details of the three censorship environments are below, increasing in 
order of censorship comprehensiveness and, therefore, difficulty to circumvent.

@@

We plan to solicit feedback on the design of this experiment at HotPETs 2015.
Specifically, we would want a reliable way to target the testing of 
specific transports. But given that the average user would not have domain knowledge of 
what transports are for Tor, is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

@@

To create a set of tasks that an average user will be able to complete reliably, 
we turned to the top Alexa sites, the most popular websites on the Internet. This 
is an indication of representative and relevant browsing behavior. To reach the final
set of website destinations, we selected sites which were popular, but also commonly
censored around the world to make our study more representative. The tasks 
associated with each website were crafted with user familiarity in mind but narrowed 
down the possibilities by removing tasks which caused ethical concerns (such as 
requiring a user to log in to a websites, which would reveal login information).  
We believe that these tasks we will use for our study will be simple tasks for an average 
user to complete, on familiar websites.

All participants will be given the same set of tasks, regardless of their environment.  
Although every participant will attempt to complete the same 
set of tasks, the difficulty of completing these tasks will vary based on their chosen environment. 
Depending on the censorship environment, some tasks may not even require the use or Tor Browser.

>>>>

\indent \indent We plan to simulate and test three distinct censorship environments
which vary in their methods of censorship and thus require distinct responses from our 
participants to circumvent successfully. These environments are designed with respect to 
common censorship techniques employed 
today, along with knowledge of how pluggable transports will need to be used.
For instance, some of Tor's pluggable transports work in places
that others do not. Additionally, some of them require additional information (like bridge 
addresses) before they work.
Details of the three censorship environments are below, increasing in 
rough order of sophistication and difficulty to circumvent.

@@

We plan to solicit feedback on the design of this experiment at the HotPETs 2015 workshop.
Specifically, we would like a reliable way to target the testing of 
specific transports. Given that the average user does not have domain knowledge of 
what transports are for Tor, we wonder whether there is anything to infer from users' selection,
or whether they are try transports at random?

@@

To create a set of tasks that an average user will be able to complete reliably, 
we turned to the top Alexa sites, the most popular websites on the Internet. This 
is an indication of representative and relevant browsing behavior. To reach the final
set of website destinations, we selected sites which were popular, but also commonly
censored around the world to make our study more representative. The tasks 
associated with each website were crafted with user familiarity in mind but narrowed 
down the possibilities by removing tasks which caused ethical concerns (such as 
requiring a user to log in with a personal account).  
We believe that the tasks we will use for our study will be easy for an average 
user to complete.

All participants will be given the same set of tasks, regardless of their environment.  
Although every participant will attempt to complete the same 
set of tasks, the difficulty of completing these tasks will vary based on the simulated censor.
Depending on the environment, some tasks may not even require the use or Tor Browser.
